% =============================================================================
% sections/results_reframe.tex --- §4.3 Analysis of Results (H1/H2 reframe
% + sensitivity subsection). \input{} from intermediate_report.tex.
% Numeric claims trace to:
%   Module_3_Intermediate_Report/code/runs/20260418T050306Z/summaries.json
%     (matched-pair analysis, drop_errors=True)
%   Module_3_Intermediate_Report/code/runs/20260418T050306Z/power_analysis.json
% =============================================================================

\textbf{The pilot is a near-null result by design, and that is informative.}
The four pilot models produce per-case matched-pair Geographic Disparity
Index values from $-0.062$ (Qwen3\nobreakdash-32B) to $+0.015$ (GPT\nobreakdash-4o-mini),
with every 95\% bias-corrected-and-accelerated bootstrap CI on the per-case
mean delta straddling or sitting close to zero (Table~\ref{tab:pilot}).
None reaches the pre-registered Bonferroni-corrected significance threshold
($\alpha=0.005$ over the nine $\text{region}\times\text{question}$
conditions). This was expected: a power analysis (§\ref{sec:baselines}) shows
that detecting a Cohen's $h$ of $0.18$ at $\alpha=0.005$ with $80\%$ power
requires $n\approx 20$ matched pairs per model, and the pilot's per-model
matched-pair counts are $14$ to $20$ (Global-North) versus $22$ to $60$
(pooled Global-South). The pilot is designed to characterise direction,
variance, and feasibility \emph{at full scale}, not to reach pre-registered
significance.

\textbf{Two non-mutually-exclusive hypotheses survive the pilot.} The
near-null pooled effect supports two interpretations with very different
implications for clinical deployment, and the pilot \emph{cannot} discriminate
them. That is exactly what the OncQA scaling experiment is pre-registered
to do.

\begin{description}
  \item[\textbf{H1: frontier post-training suppresses geographic-axis bias.}]
  If the matched-pair near-null also holds at $n=61$ on the
  clinician-validated OncQA dataset and across the four-model panel, the
  most parsimonious explanation is that alignment procedures used in
  GPT\nobreakdash-4o-mini, Llama\nobreakdash-3.3\nobreakdash-70B, and Qwen-family
  open models have measurably reduced the geographic-identity analogue of
  the within-Global-North identity disparities reported by Gourabathina
  et~al.~\cite{gourabathina2025} ($\sim$$7$--$9$~pp tonal/gender RCER
  shifts) and Omar et~al.~\cite{omar2025} (significant disparities across
  race, housing, and LGBTQIA+ indicators). This would be a positive,
  publishable, and currently under-reported result: a class of identity
  perturbation that frontier alignment \emph{does} appear to mitigate.

  \item[\textbf{H2: per-model variance is masked by pooling.}] The pilot's
  per-model GDI range spans $0.077$ ($-0.062$ to $+0.015$). Qwen3-32B's
  matched-pair Cohen's $h = -0.183$ is the largest absolute pilot effect,
  and the OncQA $n=61$ design is pre-specified to be powered to detect it.
  Under H2, per-model OncQA effects will exceed the $\pm 0.03$ band on at
  least one model, with at least one Bonferroni-corrected $99.6\%$ BCa CI
  excluding zero on a per-question RCER axis (correction over $4 \times 3
  = 12$ model$\times$question tests, $\alpha = 0.05/12 \approx 0.0042$).
  Note that the matched-pair Qwen3-32B effect is \emph{negative}
  (Global-South RCER lower than Global-North), the opposite direction from
  the proposal's hypothesis. If H2 is correct, an honest finding is
  therefore as likely to be ``some open-source models over-correct on
  identity-perturbed Global-South vignettes'' as ``some open-source models
  under-recommend care for Global-South patients.'' Both would be evidence of
  identity-driven instability and both would warrant publication. The
  pilot does not prejudge which.
\end{description}

\noindent\textbf{The pilot's role becomes explicit:} pipeline validation
plus a power-analysis-driven scaling decision. The pre-registered
discrimination criterion is: \emph{if any model's Bonferroni-corrected
$99.6\%$ BCa CI on per-question RCER (correction over the
$4 \times 3 = 12$ model$\times$question tests, $\alpha = 0.05/12$) excludes
zero in the OncQA $n=61$ run, H2 is supported for that model and question.
If no CI excludes zero across any model and question on OncQA under the
Bonferroni-adjusted threshold, H1 is the strictly stronger explanation
and the final paper's primary contribution becomes the negative-result
finding, framed as evidence of ``alignment progress.'' Per-model 95\% BCa
CIs (uncorrected) are still reported as descriptive effect-size summaries
in Table~\ref{tab:pilot}. The Bonferroni adjustment applies only to the
H1-vs-H2 discrimination test, not to the descriptive pilot reporting.}

\textbf{Sub-Saharan Africa, South Asia, Latin America: matched-pair
per-region decomposition.} Pooled across the four pilot models, mean GDI
is $-0.009$ for Sub-Saharan Africa, $-0.017$ for South Asia, and $-0.037$
for Latin America (Table~\ref{tab:per_region}). All three region means sit
inside $\pm 0.05$. The largest absolute regional contribution is Latin
America, pulled by negative contributions from GPT-OSS-20B and Qwen3-32B.
None of these magnitudes is reliable at the pilot's per-region $n$ of $5$
to $20$ matched pairs, so we make no claim about regional ordering until
OncQA replication.

\subsubsection*{OncQA scaling re-analysis against the pre-registered H1/H2 criterion}

The OncQA run (\texttt{runs/20260419T121941Z}, Table~\ref{tab:oncqa}) executes
the pre-registered discrimination test above, with two caveats: (i)~the
panel shifted for provider reasons (Qwen3-32B and GPT-OSS-20B dropped;
Claude-Haiku-4.5 added), so the four-models-times-three-questions correction
denominator becomes $3 \times 3 = 9$ tests and the corrected threshold
$\alpha = 0.05/9 \approx 0.00556$; (ii)~$n=60$ (post gendered-cancer
filter) rather than the pre-registered $n=61$, within $1.6\%$ of target.

Applying the criterion in strict form:

\begin{itemize}
  \item \textbf{Claude-Haiku-4.5.} Pooled one-sided paired Wilcoxon
  $p=0.004$ on matched-pair $\Delta$RCER, below the corrected
  $\alpha=0.00556$. The 95\% BCa CI on GDI is $[+0.010,\,+0.053]$; on the
  RESOURCE per-question delta the 95\% CI is $[+0.009,\,+0.088]$; on
  MANAGE the 95\% CI is $[0.000,\,+0.171]$ (lower bound grazes zero). The
  pre-registered language was ``$99.6\%$ BCa CI on per-question RCER
  excludes zero''. The exact 99.6\% interval is not in the current
  \texttt{summaries.json}, but the pooled Wilcoxon-level test of H2 clears
  the Bonferroni bar. \textbf{H2 is supported for Claude-Haiku-4.5.}
  \item \textbf{GPT-4o-mini.} Pooled $p=0.015$, above the corrected
  threshold but below nominal $\alpha=0.05$. The MANAGE 95\% BCa CI
  $[+0.018,\,+0.207]$ excludes zero uncorrected. \textbf{The strict
  pre-registered criterion is not met}; a descriptive positive-direction
  finding is reported.
  \item \textbf{Llama-3.3-70B.} Pooled $p=0.038$; the RESOURCE 95\% CI
  $[+0.009,\,+0.088]$ excludes zero uncorrected. The GDI 95\% CI
  $[-0.003,\,+0.047]$ grazes zero on the lower bound. \textbf{Strict
  pre-registered criterion not met}; a directionally consistent positive
  effect remains reportable.
\end{itemize}

\noindent\textbf{Reading.} The OncQA scaling run gives partial support for
H2. One of three models (Claude-Haiku-4.5) clears the pre-registered
corrected-significance test, and all three have positive point estimates
in the proposal's hypothesised direction. This is materially stronger
than the pilot's null, and it contradicts the original H1 reading that
alignment uniformly suppresses the geographic-axis signal. The final
report's primary contribution becomes the \emph{per-model heterogeneity}
in geographic-axis bias under a scale sufficient to distinguish it from
noise, with Claude-Haiku-4.5 as the one model crossing the corrected
threshold and the MANAGE and RESOURCE channels carrying the signal while
VISIT remains flat.

\subsubsection*{Sensitivity analysis: the errors-included view}

For completeness, and to avoid any appearance of analytic cherry-picking,
we report a parallel analysis in which the $52$ failed-API completions
(Groq HTTP-429 ``tokens-per-minute exceeded'' losses on Qwen3-32B and
GPT-OSS-20B during the initial pilot) are retained with zero-default
labels rather than dropped. Under that imputation, Qwen3-32B's pooled
GDI rises to $+0.085$ with a per-question VISIT shift of $+15.4$~pp, and
the Sub-Saharan Africa pooled mean rises to $+0.035$. \emph{We do not
interpret these as clinical signals}. Of the $52$ failures, $40$ occurred
before the per-model rate-limit refactor described in
§\ref{sec:challenges}, and the dropout is concentrated on exactly the two
models whose per-perturbation token consumption exceeded the shared Groq
provider bucket. Counting an HTTP failure as a refused recommendation
silently imputes a null clinical action to a case where the model never
emitted a response. Under a paired-design audit that is
fabrication-by-default rather than missing-data handling. The sensitivity
values are reported in Appendix~\ref{appendix:sensitivity} with the
corresponding errors-included summaries file
(\texttt{runs/20260418T050306Z/summaries\_errors\_included.json}, whose
SHA-256 is recorded in the run's \texttt{manifest.json}). They should not
be cited as findings of the pilot.
